### 2017-02-27 readme.Rmd
added quasirandom_covariate background points.

For a laugh, let's generate some quasirandom background points and plot them against the presence points
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
bkpts <- generate_background_points(number_of_background_points = 1000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')

```

>>>>

For a laugh, let's generate some quasirandom background points and plot them against the presence points
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
bkpts <- generate_background_points(number_of_background_points = 2000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    resolution = 2000,
                                    method = 'quasirandom_covariates')
nrow(bkpts)
```
